A large leading tail of atmospheric escape in the HAT-P-67 b system

### 2023-04-24 paper/paper1/ms.tex
Ignore the second-order effect

Second, the star's non-negligible rotational velocity sets up a configuration analogous to Doppler Tomography in the Rossiter-McLaughlin (RM) effect, but distinct in a subtle way.  Whereas traditional Doppler Tomography treats the scanning reticle as an opaque planetary disk, here the reticle resembles a transmissive filter with a wavelength center and width that varies in space and time.  We can understand this transmissive Doppler tomography effect through an example of a pathological limiting case.  Imagine the escaping atmsosphere were concentrated in a 50\% transmissive cylinder coming out of the orbital plane, as in an idealized transparent bipolar outflow.  This cyclinder would possess the planet's bulk velocity of about $-30$ km/s at the moment of transit ingress, placing the locus of absorption at about 10832.4 \AA.  But the absorptive cylinder would intercept a finite range of stellar limb velocities, broadening the apparent width of the absorption line.

>>>>

Second, the star's non-negligible rotational velocity sets up a configuration analogous to Doppler Tomography in the Rossiter-McLaughlin (RM) effect, but distinct in a subtle way.  Whereas traditional Doppler Tomography treats the scanning reticle as an opaque planetary disk, here the reticle resembles a transmissive filter with a wavelength center and width that varies in space and time.  We rank this effect as second-order and ignore it for now.
%%We can understand this transmissive Doppler tomography effect through an example of a pathological limiting case.  Imagine the escaping atmsosphere were concentrated in a 50\% transmissive cylinder coming out of the orbital plane, as in an idealized transparent bipolar outflow.  This cyclinder would possess the planet's bulk velocity of about $-30$ km/s at the moment of transit ingress, placing the locus of absorption at about 10832.4 \AA.  But the absorptive cylinder would intercept a finite range of stellar limb velocities, broadening the apparent width of the absorption line.
